---
title: "Lab 1"
subtitle: "12 September 2019"
author: "Haley Braun"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

  Name? Haley Braun
  
  What do you tell people about your field of study at a party? 
  That I started in Civil Engineering but always knew that I belonged in fashion.
  
  What are the three most important tools/strategies you use for organizing your work?
  I use a planner, phone reminders and check lists.
  
  Interesting fact about yourself?
  I have traveled to Europe a few times and spent time in Italy with my whole family.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
