---
title: "Lab 1"
subtitle: "12 September 2019"
author: "Haley Braun"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

  Name? Haley Braun
  
  What do you tell people about your field of study at a party? 
  That I started in Civil Engineering but always knew that I belonged in fashion.
  
  What are the three most important tools/strategies you use for organizing your work?
  I use a planner, phone reminders and check lists.
  
  Interesting fact about yourself?
  I have traveled to Europe a few times and spent time in Italy with my whole family.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Understanding Concepts

  1. Explain the difference between Git and Github.
  Git is on your local computer aned Github is where you can collaborate and share files that can be seen by anyone or edited by anyone given access.
  
  2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 
  Yes. We want to share work with others and its easy to backup your work on Github. Advantage is sharing with others and having your work backed up. The disadvantage is that there is a learning curve when learning Git and GitHub.

  3. What is a repository in Git and how can you create a repository in Git (write out the command(s))? 
  A storage space for your files and it tracks the history of your files. git knit, git add, git commit.
  
## Coding Exercises
You may work on this with your partner or individually. 

  1. Write code to count the total number of `NA` occurrences in the vector `X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.
  
```{r}
  x = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
  length(which(is.na(x)))
```
  

  2. Run the following code: 

```{r}
   age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
   weight[3] = 150
   weight
```
   
  This code took three vectors (`age`, `smoker`, and `weight`) and binded them together into an `R` object known as a 
  `data.frame`. The advantage of `data.frame` is that it can handle vectors of different types. For example, age is a numeric 
    vector but smoker status is a character vector (T or F). We named this `data.frame` as `example_data`. I obviously made a
    data entry error: someone cannot have 0 weight. The correct weight should be 150 pounds. Write one line of code that can
    easily correct this using the `[]` syntax. 


  3. In the following I have two code snippets. Turn these code snippets into functions. Think about what each function does
  and what you would name it. How many arguments does it need?
  
```{r, eval=FALSE}
  na_mean = function(vector) {
    return(mean(is.na(x)))
  }
```
  Just one argument
```{r}
   percentageofsum = function(vector) {
    return(x / sum(x, na.rm = TRUE))
}
```
  
  
4. Write a function named `both_na()`. This function take two vectors of the same length and returns the number of positions that have an `NA` value in both vectors. 
```{r}
  both_na = function(v1,v2){
    x = v1[which(is.na(v2))]
    return(length(which(is.na(x))))
}
